A Simplified Spectral Deferred Correction Method for Coupling Hydrodynamics with Reaction Networks and Nuclear Statistical Equilibrium

### 2020-10-23 simplified_sdc_intro/paper.tex
add more comparisons

@@

>>>>

\begin{deluxetable}{lllllll}
\tablecaption{\label{table:react_convert_strang} Convergence ($L_1$ norm) for the reacting convergence problem using Strang splitting.}
\tablehead{\colhead{field} & \colhead{$\epsilon_{64 \rightarrow 128}$} & 
           \colhead{rate} & \colhead{$\epsilon_{128\rightarrow 256}$} & 
           \colhead{rate} & \colhead{$\epsilon_{256\rightarrow 512}$}}
\startdata
 $\rho$                      & $2.781 \times 10^{18}$  & 2.051  & $6.711 \times 10^{17}$  & 2.580  & $1.122 \times 10^{17}$  \\
 $\rho u$                    & $6.781 \times 10^{26}$  & 2.445  & $1.245 \times 10^{26}$  & 2.907  & $1.659 \times 10^{25}$  \\
 $\rho v$                    & $6.781 \times 10^{26}$  & 2.445  & $1.245 \times 10^{26}$  & 2.907  & $1.659 \times 10^{25}$  \\
 $\rho E$                    & $2.465 \times 10^{35}$  & 2.333  & $4.892 \times 10^{34}$  & 2.650  & $7.794 \times 10^{33}$  \\
 $\rho e$                    & $2.268 \times 10^{35}$  & 2.298  & $4.610 \times 10^{34}$  & 2.722  & $6.988 \times 10^{33}$  \\
 $T$                         & $2.248 \times 10^{21}$  & 1.682  & $7.003 \times 10^{20}$  & 2.439  & $1.291 \times 10^{20}$  \\
 $\rho X(\isotm{He}{4})$     & $2.862 \times 10^{18}$  & 2.027  & $7.023 \times 10^{17}$  & 2.554  & $1.196 \times 10^{17}$  \\
 $\rho X(\isotm{C}{12})$     & $1.717 \times 10^{17}$  & 1.945  & $4.460 \times 10^{16}$  & 2.194  & $9.745 \times 10^{15}$  \\
 $\rho X(\isotm{O}{16})$     & $1.718 \times 10^{14}$  & 1.648  & $5.482 \times 10^{13}$  & 1.898  & $1.471 \times 10^{13}$  \\
 $\rho X(\isotm{Fe}{56})$    & $2.781 \times 10^{8}$   & 2.051  & $6.711 \times 10^{7}$   & 2.580  & $1.122 \times 10^{7}$   \\
\enddata
\end{deluxetable}

\begin{deluxetable}{lllllll}
\tablecaption{\label{table:react_convert_strang} Convergence ($L_1$ norm) for the reacting convergence problem using Strang splitting with $T$ evolution disabled.}
\tablehead{\colhead{field} & \colhead{$\epsilon_{64 \rightarrow 128}$} & 
           \colhead{rate} & \colhead{$\epsilon_{128\rightarrow 256}$} & 
           \colhead{rate} & \colhead{$\epsilon_{256\rightarrow 512}$}}
\startdata
 $\rho$                      & $2.735 \times 10^{18}$  & 2.057  & $6.571 \times 10^{17}$  & 2.474  & $1.183 \times 10^{17}$  \\
 $\rho u$                    & $6.729 \times 10^{26}$  & 2.416  & $1.260 \times 10^{26}$  & 2.699  & $1.941 \times 10^{25}$  \\
 $\rho v$                    & $6.729 \times 10^{26}$  & 2.416  & $1.260 \times 10^{26}$  & 2.699  & $1.941 \times 10^{25}$  \\
 $\rho E$                    & $2.513 \times 10^{35}$  & 2.226  & $5.372 \times 10^{34}$  & 2.169  & $1.195 \times 10^{34}$  \\
 $\rho e$                    & $2.292 \times 10^{35}$  & 2.194  & $5.011 \times 10^{34}$  & 2.253  & $1.051 \times 10^{34}$  \\
 $T$                         & $2.321 \times 10^{21}$  & 1.606  & $7.623 \times 10^{20}$  & 1.993  & $1.915 \times 10^{20}$  \\
 $\rho X(\isotm{He}{4})$     & $2.806 \times 10^{18}$  & 2.028  & $6.880 \times 10^{17}$  & 2.432  & $1.275 \times 10^{17}$  \\
 $\rho X(\isotm{C}{12})$     & $1.807 \times 10^{17}$  & 1.846  & $5.026 \times 10^{16}$  & 1.605  & $1.653 \times 10^{16}$  \\
 $\rho X(\isotm{O}{16})$     & $1.905 \times 10^{14}$  & 1.500  & $6.737 \times 10^{13}$  & 1.439  & $2.484 \times 10^{13}$  \\
 $\rho X(\isotm{Fe}{56})$    & $2.735 \times 10^{8}$   & 2.057  & $6.571 \times 10^{7}$   & 2.474  & $1.183 \times 10^{7}$   \\
\enddata
\end{deluxetable}

@@

\begin{deluxetable}{lllllll}
\tablecaption{\label{table:nse_strang_methodI} Convergence ($L_1$ norm) for the NSE convergence
problem using Strang splitting + Method I.}
\tablehead{\colhead{field} & \colhead{$\epsilon_{64 \rightarrow 128}$} & 
           \colhead{rate} & \colhead{$\epsilon_{128\rightarrow 256}$} & 
           \colhead{rate} & \colhead{$\epsilon_{256\rightarrow 512}$}}
\startdata
 $\rho$                      & $4.301 \times 10^{19}$  & 1.348  & $1.690 \times 10^{19}$  & 1.166  & $7.532 \times 10^{18}$  \\
 $\rho u$                    & $1.866 \times 10^{28}$  & 1.429  & $6.929 \times 10^{27}$  & 1.101  & $3.230 \times 10^{27}$  \\
 $\rho v$                    & $1.866 \times 10^{28}$  & 1.429  & $6.929 \times 10^{27}$  & 1.101  & $3.230 \times 10^{27}$  \\
 $\rho E$                    & $1.781 \times 10^{38}$  & 1.053  & $8.585 \times 10^{37}$  & 1.021  & $4.231 \times 10^{37}$  \\
 $\rho e$                    & $1.781 \times 10^{38}$  & 1.053  & $8.583 \times 10^{37}$  & 1.021  & $4.230 \times 10^{37}$  \\
 $T$                         & $6.853 \times 10^{21}$  & 1.044  & $3.325 \times 10^{21}$  & 1.018  & $1.642 \times 10^{21}$  \\
 $\rho X(\isotm{He}{4})$     & $1.070 \times 10^{18}$  & 1.186  & $4.701 \times 10^{17}$  & 1.051  & $2.269 \times 10^{17}$  \\
 $\rho X(\isotm{C}{12})$     & $2.166 \times 10^{12}$  & 1.533  & $7.482 \times 10^{11}$  & 1.189  & $3.283 \times 10^{11}$  \\
 $\rho X(\isotm{O}{16})$     & $1.244 \times 10^{13}$  & 1.396  & $4.727 \times 10^{12}$  & 1.117  & $2.179 \times 10^{12}$  \\
 $\rho Y_e$                  & $2.442 \times 10^{19}$  & 1.442  & $8.990 \times 10^{18}$  & 1.212  & $3.880 \times 10^{18}$  \\
 $\rho \bar{A}$              & $1.055 \times 10^{22}$  & 1.032  & $5.158 \times 10^{21}$  & 1.022  & $2.541 \times 10^{21}$  \\
 $\rho (B/A)$                & $4.512 \times 10^{20}$  & 1.386  & $1.727 \times 10^{20}$  & 1.207  & $7.479 \times 10^{19}$  \\
\enddata
\end{deluxetable}

\begin{deluxetable}{lllllll}
\tablecaption{\label{table:nse_strang_methodII} Convergence ($L_1$ norm) for the NSE convergence
problem using Strang splitting + Method II.}
\tablehead{\colhead{field} & \colhead{$\epsilon_{64 \rightarrow 128}$} & 
           \colhead{rate} & \colhead{$\epsilon_{128\rightarrow 256}$} & 
           \colhead{rate} & \colhead{$\epsilon_{256\rightarrow 512}$}}
\startdata
 $\rho$                      & $4.522 \times 10^{19}$  & 1.659  & $1.432 \times 10^{19}$  & 1.542  & $4.917 \times 10^{18}$  \\
 $\rho u$                    & $1.883 \times 10^{28}$  & 1.681  & $5.873 \times 10^{27}$  & 1.524  & $2.042 \times 10^{27}$  \\
 $\rho v$                    & $1.883 \times 10^{28}$  & 1.681  & $5.873 \times 10^{27}$  & 1.524  & $2.042 \times 10^{27}$  \\
 $\rho E$                    & $5.933 \times 10^{37}$  & 1.613  & $1.940 \times 10^{37}$  & 1.411  & $7.293 \times 10^{36}$  \\
 $\rho e$                    & $5.931 \times 10^{37}$  & 1.613  & $1.939 \times 10^{37}$  & 1.411  & $7.291 \times 10^{36}$  \\
 $T$                         & $9.885 \times 10^{20}$  & 1.207  & $4.281 \times 10^{20}$  & 1.058  & $2.057 \times 10^{20}$  \\
 $\rho X(\isotm{He}{4})$     & $5.086 \times 10^{17}$  & 1.430  & $1.887 \times 10^{17}$  & 1.187  & $8.288 \times 10^{16}$  \\
 $\rho X(\isotm{C}{12})$     & $1.585 \times 10^{12}$  & 1.829  & $4.462 \times 10^{11}$  & 1.433  & $1.652 \times 10^{11}$  \\
 $\rho X(\isotm{O}{16})$     & $8.060 \times 10^{12}$  & 1.706  & $2.470 \times 10^{12}$  & 1.347  & $9.710 \times 10^{11}$  \\
 $\rho Y_e$                  & $2.379 \times 10^{19}$  & 1.678  & $7.431 \times 10^{18}$  & 1.578  & $2.489 \times 10^{18}$  \\
 $\rho \bar{A}$              & $5.141 \times 10^{21}$  & 1.230  & $2.191 \times 10^{21}$  & 1.087  & $1.032 \times 10^{21}$  \\
 $\rho (B/A)$                & $4.149 \times 10^{20}$  & 1.693  & $1.283 \times 10^{20}$  & 1.562  & $4.345 \times 10^{19}$  \\
\enddata
\end{deluxetable}
